March Madness Basketball Turniment

### 2021-04-16 slides/slides.Rmd
fixed typo

merged <- readr::read_csv(here::here("data", "merged.csv"))
ids <- readr::read_csv(here::here("data", "ids.csv"))
s2021 <- readr::read_csv(here::here("data", "s2021.csv"))
source(here::here("R", "fitting.R"))
theme_set( theme_light(base_size = 25))
```

>>>>

merged <- readr::read_csv(here::here("data", "merged.csv"))
ids <- readr::read_csv(here::here("data", "ids.csv"))
s2021 <- readr::read_csv(here::here("data", "s2021.csv"))
source(here::here("R", "fitting.R"))
theme_set(theme_light(base_size = 25))
```
